%-------------------------
% Resume in Latex
% Author : Ankit Jangwan
% Based off of: https://github.com/sb2nov/resume
% Template variant: Jake Gutierrez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\input{glyphtounicode}
\newcommand{\phone}[1]{\href{tel:#1}{\faPhone{} #1}}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins (Jake template)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS-readable PDF
\pdfgentounicode=1

%-------------------------
% Custom commands (Jake variant)
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ankitjang.one/}{\Large Ankit Jangwan}} & Email : \href{mailto:ankit@ankitjang.one}{ankit@ankitjang.one}\\
  \href{https://ankitjang.one/}{https://ankitjang.one} & Mobile : +91-9761370345 \\
  \href{https://www.linkedin.com/in/ankit-jangwan-969419141/}{LinkedIn: ankit-jangwan-969419141} & \href{https://github.com/jangwanAnkit}{GitHub: jangwanAnkit} \\
\end{tabular*}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Graphic Era University}{Dehradun, Uttarakhand}
      {B.Tech in Computer Science}{Jul. 2016 -- May 2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer II}{Remote, India}
      {Instahyre}{Jan. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Working on the employer side of Instahyre’s recruitment platform with focus on candidate screening, activities, notes, interview scheduling, and evaluations.}
        \resumeItem{\textbf{Tech stack:} Angular and Django for end-to-end feature development, bug fixing, and performance tuning.}
        \resumeItem{\textbf{Performance:} Migrated Django templates to Jinja, improving page load time from $\sim$1000 ms to $<$200 ms, and optimized key APIs using SQL optimisations, async tasks, and refactoring.}
        \resumeItem{\textbf{Collaboration:} Built an enhanced candidate view, mentored SDE I engineers, led code reviews, and handled production issue debugging with Datadog, Sentry, and logs.}
      \resumeItemListEnd

    \resumeSubheading
      {Business Integration Specialist}{Remote, India}
      {Cloudify}{Aug. 2024 -- Dec. 2024}
      \resumeItemListStart
        \resumeItem{Led the Custom Integration team, owning development lifecycle from requirements to deployment.}
        \resumeItem{Built and deployed Django, Express, React, and Next.js apps on Azure and AWS.}
        \resumeItem{Implemented integrations such as Amazon SES, MSG91, Stripe, Celery/Redis task queues, and custom Shopify/WooCommerce solutions.}
      \resumeItemListEnd

\resumeSubheading
  {Saara Inc}{Remote, India}
  {Lead Software Developer}{May 2023 -- Aug. 2024}
  \resumeItemListStart
    \resumeItem{Led multiple projects, including a greenfield product, from product discussions through architecture, backend/frontend implementation, and cloud deployments.}
    \resumeItem{Worked with Django, React, Next.js, TypeScript, and Azure, plus relevant AWS services, to deliver customer-facing features at scale.}
  \resumeItemListEnd

\resumeSubSubheading
  {Software Developer}{May 2022 -- Apr. 2023}
  \resumeItemListStart
    \resumeItem{Contributed as a backend developer and expanded into frontend work using HTML, CSS, JavaScript, and React.}
    \resumeItem{Implemented integrations including Amazon SES, MSG91, Celery/Redis, and Shopify/WooCommerce APIs for custom e-commerce solutions.}
  \resumeItemListEnd


    \resumeSubheading
      {Software Engineer}{Remote, India}
      {SHL}{Jul. 2020 -- May 2022}
      \resumeItemListStart
        \resumeItem{Worked on multiple Reporting and Scoring web applications as a backend developer using Python and PHP.}
        \resumeItem{Improved reporting engine efficiency by 30\% by refactoring legacy code and optimising queries.}
        \resumeItem{Delivered custom reporting and scoring for clients such as NASSCOM and Adecco and contributed to migration to a universal reporting platform.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://saara.io/salesgpt/}{SalesGPT} -- Saara Inc} $|$ \emph{Python, Django, React, PostgreSQL, Azure}}{Feb. 2023 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{Built a virtual sales assistant for online stores on top of OpenAI, designing the backend from scratch and implementing an interactive chatbot UI.}
      \resumeItemListEnd
      \resumeProjectHeading
  {\textbf{Message Scheduler} $|$ \emph{Python, Django, Celery, Redis, Telegram Bot API, Email APIs}}{2024 -- Present}
  \resumeItemListStart
    \resumeItem{Built an automated message scheduling system supporting both email and Telegram delivery with cron-based job execution for recurring notifications.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{MeetAssist Chrome Extension} $|$ \emph{JavaScript, Chrome Extension APIs, Google Calendar API}}{2023 -- 2024}
  \resumeItemListStart
    \resumeItem{Developed a Chrome extension for calendar management and meeting notes automation, integrating with Google Calendar to streamline meeting workflows.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Personal Portfolio Website} $|$ \emph{HTML, CSS, JavaScript, Domain Management}}{2023 -- Present}
  \resumeItemListStart
    \resumeItem{Built and deployed a personal portfolio website at \href{https://ankitjang.one}{ankitjang.one} to showcase projects and technical expertise.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
